Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
adding \.
Remove comment about verify
QuickCheck can not verify anything, it can only try to find a counter
example.
brushing up Hspec section.

One problem of the original Hspec is that it still uses HUnit
assertions (e.g. verb|@?=| in the example above) , which are TDD
terminologies. In BDD, they are replaced with design terminologies,
{\it expectation}.
The following Rspec example shows the ``should'' expectation keyword:

@@

\begin{quote}
    TBD:
\begin{itemize}
    \item RSpec provides a mechanism to expect exceptions.

        \begin{verbatim}
expect {launch_missiles}.to raise_error
        \end{verbatim}

        Hspec does not yet provide a mechanism to set expectations
        about the outcome of examples.  It uses HUnit assertions
        instead.

        HUnit does not provide a mechanism to expect exceptions.

    \item \emph{optional:} Motivate why it's important to integrate
        Doctest with
        Cabal.

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    evidence with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for user documentation.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology
\end{itemize}

@@

\begin{quote}
    sol: Should we use verify instead of test here?
\end{quote}

>>>>

The problem of the original Hspec is that it does not provide
a mechanism to express \emph{expectation}\/s with
BDD terminology.
For instance,
it still uses HUnit
assertions (e.g. \verb|@?=| in the example above), which are TDD
terminologies. In BDD, they are replaced with design terminologies.
The following Rspec example shows the ``should'' expectation keyword:

@@

\noindent Another example is exceptions. Hspec does not yet provide a
mechanism to express expectation on exceptions. The following is
how to express expectation on an exception in Rspec:

\begin{quote}
\small
\begin{verbatim}
expect {launch_missiles}.to raise_error
\end{verbatim}
\end{quote}

\begin{quote}
    TBD:
\begin{itemize}
    \item \emph{optional:} Motivate why it's important to integrate
        Doctest with
        Cabal.

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    evidence with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for user documentation.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\end{itemize}

@@
